\documentclass[a4]{article}
\usepackage{fullpage}
\usepackage{needspace}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\textheight=10in
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

\usepackage{color,soul}
%\pagestyle{empty}

% \raggedbottom
\raggedright

% \renewcommand{\encodingdefault}{cg}
% \renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{
  \vspace*{-9pt}
  \begin{verse}
    \textbf{#1} #2
  \end{verse}
}

\newcommand{\lineunder}{
  \vspace*{-8pt} \\
  \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header}[1]{
  {\hspace*{-15pt}\vspace*{6pt} \textsc{#1}}
  \vspace*{-6pt} \lineunder
}

\newcommand{\employer}[3]{
  {
    \textbf{#1} (#2)\\
    \underline{\textbf{\emph{#3}}}\\
  }
}

\newcommand{\repo}[3]{
  {
    \underline{{\textbf{\href{#2}{#1}}}}\\
    \emph{#3}\\[0.2cm]
  }
}

\newcommand{\subheader}[1]{
  {\underline{\textbf{\emph{#1}}}\\}
}

\newcommand{\contact}[3]{
  \vspace*{-8pt}
  \begin{center}{
      \LARGE \scshape {#1}}\\ #2 \lineunder #3
  \end{center}
  \vspace*{-8pt}
}

\newenvironment{achievements}{
  \begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}
}
{
  \vspace*{4pt}
  \end{list}
}

\newcommand{\schoolwithcourses}[4]{
  \textbf{#1} #2 \\ #3\\ #4 \\ Selected Coursework:\\
  \vspace*{5pt} } \newcommand{\school}[4]{ \textbf{#1} #2 $\bullet$ #3\\ #4
  \\
}
% END RESUME DEFINITIONS




\begin{document}

\small
\smallskip
\vspace*{-44pt}

\contact{Alejandro g\'omez} { alegomez544@gmail.com $\bullet$ agomezl@eafit.edu.co }

\bigskip
\header{Education}

\schoolwithcourses{EAFIT University (Medell\'in, Colombia) \\ Computer
  Science}{} {2010-2015} {Final Cumulative (GPA): 4.31/5}
\area{Computer Science: }{ Networking $\cdot$ Databases $\cdot$ Data
  structures and algorithms $\cdot$ Numerical analysis $\cdot$
  Operating systems $\cdot$ Computer architecture $\cdot$ Compilers
  $\cdot$ Software engineering $\cdot$ Automata and formal languages
  $\cdot$ Programing paradigms $\cdot$ Functional programming $\cdot$
  Artificial intelligence} \area{Mathematics: }{Multivariable calculus
  $\cdot$ Linear algebra $\cdot$ Discrete math $\cdot$ Statistics
  $\cdot$ Real analysis}

\bigskip
\header{Work History}

\employer{EAFIT University (Medell\'in, Colombia) \\ Teacher assistant
  of Automata and formal languages \\}{July~2013 - November~2013 $\bullet$ July~2015 - Current}
{T.A of Automata and formal languages}

\bigskip

\employer{Purdue University (Indiana, United States) \\ SURF(Summer Undergraduate Research Fellowships)}
{May 2013 - August 2013}{Research on nanoscale simulations}

\bigskip

\employer{Purdue University (Indiana, United States) \\ Internship at NCN}{July 2014 - January 2015}
{Internship at Network for Computational Nanotechnology}

\bigskip

\employer{Apolo (High Performance Computing facility ) EAFIT
  University (Medell\'in, Colombia) \\ Student Research assistant}{July 2012 -
  November 2015 }{Part-time Student Research assistant}

\bigskip

\employer{Trustworthy Systems Research Group CSIRO/Data61 (Sydney, Australia)\\
          Proof Engineer}
         {February 2016 - Current}{Proof Engineer}

\bigskip


\header{Skills}
\begin{achievements}
\item Proficient in Haskell
\item Proficient with GNU/Linux Systems an tools.
\item Proficient in Bash.
\item Proficient in \LaTeX.
\item Familiar with Agda (dependently typed functional programming).
\item Familiar with TPTP/TSTP (automated theorem proving).
\item Familiar with C++, C, MPI.
\item Familiar with GNU/Make.
\end{achievements}

\needspace{4\baselineskip}
\header{Languages}
\begin{achievements}
\item Spanish - (Native)
\item English - (TOEIC 855)
\end{achievements}

\newpage

\header{Achievements}
\begin{achievements}
\item Talk - An Introduction to Erlang. Logic and computation seminar. U. EAFIT. March. 8.
  (\href{http://agomezl.github.io/slides/erlang.pdf}{Slides})
\item Talk - Idris: A language with dependent types
  (\href{http://agomezl.github.io/slides/Idris.pdf}{Slides})
\item Research - Proof Reconstruction: Parsing Proofs
 (\href{https://repository.eafit.edu.co/handle/10784/5484}{Draft})
\item Participation - Student Cluster Competition (
  \href{http://sc14.supercomputing.org/engage/hpc-interconnections/sc14-student-cluster-competition}
  {SCC 14}) New Orleans, LA, United States.
\item Participation - Student Cluster Competition (
\href{http://www.hpcadvisorycouncil.com/events/2015/isc15-student-cluster-competition/team_purdue_eafit.php}
  {ISC 15}) Frankfurt, Germany.
\item Participation - Student Cluster Competition (
  \href{http://sc15.supercomputing.org/conference-program/student-programs/sc15-student-cluster-competition}
  {SCC 15}) Austin, TX, United States.
\end{achievements}

\bigskip
\header{Miscellaneous}
\begin{achievements}
\item Emacs enthusiast.
\item Longboard rider.
\item Science fiction literature fan.
\end{achievements}

\end{document}
